My title

### 2024-11-27 paper/paper.qmd
fixed introduction

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
print(data)
```

@@

@@

@@

\newpage
```{r}
#| label: summary_statistic_cleaned_dataset
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

@@

@@

```{r}
#| label: summary_statistic_cleaned_dataset
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
#| layout-ncol: 3

@@

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the rating of childrens' books using the . By using logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not. The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature"
format: pdf
number-sections: true
bibliography: references.bib
---

@@

data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
```

@@

## Estimand

# Model

# Results

# Discussion

# Appendix

@@

```{r}
#| label: summary_statistic_cleaned_dataset2
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

\newpage
```{r}
#| label: summary_statistic_cleaned_dataset3
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

```{r}
#| label: summary_statistic_cleaned_dataset4
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

```{r}
#| label: summary_statistic_cleaned_dataset5
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

@@

```{r}
#| label: summary_statistic_cleaned_dataset6
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
#| layout-ncol: 3

@@

```{r}
#| label: summary_statistic_cleaned_dataset7
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false
